Atypical Lyman-$\alpha$ emission in a dwarf galaxy via multiphase gas and rotation.

### 2017-01-19 paper/letter.tex
abstract
secciones

\begin{abstract}
Example.
\end{abstract}

@@

  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe.    
Before the observational detection of the first galaxies becomes
reality, CDGs are the best systems to test our ideas on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad symmetric Lyman-$\alpha$ line emission that had evaded theoretical
interpretation so far. 
In this letter we explain these features by two different models: an
homogeneous gaseous sphere undergoing bulk rotation and an interstellar
medium composed by outflowing clumps with additional random motions.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these physical conditions.
We find that both models independently require high velocities
(either a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$ or a clump velocity
dispersion of \sigmaclump with outflows of
\inftyclump) consistent with a dynamical mass of at
least a billion solar masses, ten times larger than its baryonic mass.   
We argue that a possible explanation for this excess of
dynamical mass is the presence of a supermassive black hole at the
center of \tol. 
This work demonstrates the importance of considering multiphase
physics and rotation among the possible conditions shaping the
\lya\ spectra of the first galaxies.  
Additionally, if future kinematic maps of \tol\ confirm the high
velocities postulated in our model, it would provide new
evidence for dwarf galaxies as hosts of supermassive black
holes.

@@

In this letter we show how the \tol's \lya\ profile can be explained
either by rotation \citep{GaravitoCamargo2014} or the recently developed
class of more complex 
multiphase models that predict a wider variety of spectra
including, single, double and triply peaked spectra \citep{Gronke2016}.  
Figure 1. summarizes our findings.
Dots represent the observational data for \tol\ with the
overplot from our best fits from the analytical solution for a
rotating homogeneous gas sphere (thin line) and the multiphase
model (thick line). 
This is the first time that these models have been introduced with
success to explain an observed \lya\ profile.

@@

@@

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{CLARA-TOL-main.pdf}
\caption{{\bf Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.}
  Dots correspond to the observational data. The line shows the results
of our best model from a full radiative transfer simulation both for
the rotation and multiphase models.} 
\end{center}
\end{figure*}

\section*{\tol\ characteristics}

\section*{The Rotation Model}

The rotation model corresponds to the work presented in
\citep{GaravitoCamargo2014} based on the Monte Carlo code
\texttt{CLARA} \citep{CLARA}. 
In that model the Ly-$\alpha$ photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the HI line's
center optical  depth $\tau$ measured from the center to its surface, the HI
temperature $T$, and the linear surface velocity $V_{\rm max}$.  
Photons are emitted at their natural frequency from the center of the
sphere. 
Including the effect of dust only changes the overall line
normalization but not its shape.  
The results we report in the main body of the paper do not include any
dust model.
In this letter we use an analytical solution that captures the most
important effects of rotation onto the \lya\ line.

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{emcee_results.pdf}
\caption{{\bf Results from the Markov Chain Monte Carlo computation for
    the rotation model.} The dotted vertical lines in the outer histograms 
	represent the 16th, 50th and 84th percentiles. \label{emceeresults}} 
\end{center}
\end{figure*}

\section*{The Multiphase Model}

In order to map out this large parameter space, we randomly drew
$2500$ sets of parameters within a observationally realistic range
(based on the considerations of \citep{Laursen2013ApJ...766..124L})
yielding a large variety of single-, double- and triple-peaked
spectra. 
The full analysis of the the spectral features as well as
more details on the radiative transfer are presented in
\citep{Gronke2016}.    
 For the current work, we computed the $\chi^2$ for each of the $2500$
models. We selected the best $50$ models with the lowest $\chi^2$. The
$\chi^2$ gap in those $50$ models is close to $3000$, the lowest
$\chi^2$ is close to $1200$. The total number of degrees of freedom is
$104$.

\section*{Dynamical Mass Estimates}

As described in the main the letter, we use the 3D half-luminosity
radius, $r_{s}$, as the typical size for the HI region.

>>>>

\begin{abstract}
  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe.    
Before the observational detection of the first galaxies becomes
reality, CDGs are the best systems to test our ideas on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad symmetric Lyman-$\alpha$ line emission that had evaded theoretical
interpretation so far. 
In this paper we explain these features by two different models: an
homogeneous gaseous sphere undergoing bulk rotation and an interstellar
medium composed by outflowing clumps with additional random motions.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these physical conditions.
We find that both models independently require high velocities
(either a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$ or a clump velocity
dispersion of \sigmaclump with outflows of
\inftyclump) consistent with a dynamical mass of at
least a billion solar masses, ten times larger than its baryonic mass.   
We argue that a possible explanation for this excess of
dynamical mass is the presence of a supermassive black hole at the
center of \tol. 
This work demonstrates the importance of considering multiphase
physics and rotation among the possible conditions shaping the
\lya\ spectra of the first galaxies.  
Additionally, if future kinematic maps of \tol\ confirm the high
velocities postulated in our model, it would provide new
evidence for dwarf galaxies as hosts of supermassive black
holes.  
\end{abstract}

@@

@@

In this paper we show how the \tol's \lya\ profile can be explained
either by rotation \citep{GaravitoCamargo2014} or the recently developed
class of more complex 
multiphase models that predict a wider variety of spectra
including, single, double and triply peaked spectra \citep{Gronke2016}.

\section{\tol}

\section{Theoretical Models}

\subsection{Rotation Model}

The rotation model corresponds to the work presented in
\citep{GaravitoCamargo2014} based on the Monte Carlo code
\texttt{CLARA} \citep{CLARA}. 
In that model the Ly-$\alpha$ photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the HI line's
center optical  depth $\tau$ measured from the center to its surface, the HI
temperature $T$, and the linear surface velocity $V_{\rm max}$.  
Photons are emitted at their natural frequency from the center of the
sphere. 
Including the effect of dust only changes the overall line
normalization but not its shape.  
The results we report in the main body of the paper do not include any
dust model.
In this paper we use an analytical solution that captures the most
important effects of rotation onto the \lya\ line.

\subsection{Multiphase Model}

In order to map out this large parameter space, we randomly drew
$2500$ sets of parameters within a observationally realistic range
(based on the considerations of \citep{Laursen2013ApJ...766..124L})
yielding a large variety of single-, double- and triple-peaked
spectra. 
The full analysis of the the spectral features as well as
more details on the radiative transfer are presented in
\citep{Gronke2016}.

\section{Results}

\begin{figure*}
\begin{center}
\includegraphics[width=0.7\textwidth]{CLARA-TOL-main.pdf}
\caption{{\bf Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.}
  Dots correspond to the observational data. The line shows the results
of our best model from a full radiative transfer simulation both for
the rotation and multiphase models.} 
\end{center}
\end{figure*}

Figure 1. summarizes our findings.
Dots represent the observational data for \tol\ with the
overplot from our best fits from the analytical solution for a
rotating homogeneous gas sphere (thin line) and the multiphase
model (thick line). 
This is the first time that these models have been introduced with
success to explain an observed \lya\ profile.

@@

 For the current work, we computed the $\chi^2$ for each of the $2500$
models. We selected the best $50$ models with the lowest $\chi^2$. The
$\chi^2$ gap in those $50$ models is close to $3000$, the lowest
$\chi^2$ is close to $1200$. The total number of degrees of freedom is
$104$.

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{emcee_results.pdf}
\caption{Results from the Markov Chain Monte Carlo computation for
    the rotation model. The dotted vertical lines in the outer histograms 
	represent the 16th, 50th and 84th percentiles. \label{emceeresults}} 
\end{center}
\end{figure*}

\section{Interpretation}

\subsection{Dynamical Mass Estimates}

We use the 3D half-luminosity
radius, $r_{s}$, as the typical size for the HI region.

@@

\section{Conclusions}

@@
